### 2025-11-10 simulation.qmd
20251110 - additions and clarification

@@

Third, we analyze the simulated data.
For each iteration of the simulation, the `Analyse()` function will return a vector with a requested variables: player (`id`), their simulated mean (`mean_pts`) and standard deviation (`sd_pts`) of projected fantasy points across sources, their the 10th (`q10`) and 90th (`q90`) quartiles of their distributions of projected points, and the simulated probability of the player scoring at least 100 (`p100`), 150 (`p150`), 200 (`p200`), 250 (`p250`), 300 (`p300`), and 350 (`p350`) fantasy points.
We then combine all the rows into a tibble dataframe, with each player as a different row.
A separate dataset is created for each of the simulation replications.

>>>>

In this example, we simulate players' likely distribution of (projected) fantasy points based on bootstrapping players' projected statisics (e.g., passing yards, passing touchdowns).
That is, for each iteration of the bootstrap, we randomly draw a projected value from a projection source (with replacement), for each of various statistical categories.
For instance, assume we have 10 projection sources for Tom Brady.
In iteration 1, we may draw Brady's projected passing yards from ESPN and projected passing touchdowns from numberFire (i.e., randomly selected projection sources).
In iteration 2, we may draw Brady's projected passing yards from Yahoo and projected passing touchdowns from CBS (i.e., randomly selected projection sources).
We do this for many iterations.
We can compute projected fantasy points at each iteration and then summarize the distribution of fantasy points for Tom Brady (and all players) across all iterations.
This bootstrap simulation is valuable because it would give us a fuller distribution of the likely range of players' performance than just the mean (or range) of projected points across sources.

@@

Third, we analyze the simulated data.
For each iteration of the simulation, the `Analyse()` function will return a vector with a requested variables: player (`id`), their simulated mean (`mean_pts`) and standard deviation (`sd_pts`) of projected fantasy points across sources, the 10th (`q10`) and 90th (`q90`) quartiles of their distributions of projected points, and the simulated probability of the player scoring at least 100 (`p100`), 150 (`p150`), 200 (`p200`), 250 (`p250`), 300 (`p300`), and 350 (`p350`) fantasy points.
We then combine all the rows into a tibble dataframe, with each player as a different row.
A separate dataset is created for each of the simulation replications.
